### 2024-02-14 parts/intro.tex
typo

The approach taken in this paper avoids leveraging tools from the theory of
factorizations forests in finite monoids \cite{simon90}, which has been the
traditional method used to understand (commutative output) \kl{polyregular
functions} \cite{doueneau2021pebble,doueneau2022hiding,LOPEZ23b}, and instead
focus on intrinsic description of the functions themselves (via canonical
computational models such as the \kl{residual transducer} of
\cref{residual-transducer:def}, or explicit encoding/decoding into polynomials
via \cref{decompose-polynomial:lem}).

>>>>

The approach taken in this paper avoids the use of tools from the theory of
factorizations forests in finite monoids \cite{simon90}, which has been the
traditional method used to understand (commutative output) \kl{polyregular
functions} \cite{doueneau2021pebble,doueneau2022hiding,LOPEZ23b}, and instead
focuses on intrinsic description of the functions themselves (via canonical
computational models such as the \kl{residual transducer} of
\cref{residual-transducer:def}, or explicit encoding/decoding into polynomials
via \cref{decompose-polynomial:lem}).
